Local Spectral Clustering of Density Upper Level Sets

### 2019-01-18 icml/icml_local_density_clustering.tex
began restructuring proof of theorem 2
completed re-organization of Theorem 2

\begin{abstract}
	Spectral clustering methods are 
	a family of popular non-parametric clustering tools.
	Recent works have proposed and analyzed 
	\emph{local} spectral methods, which 
	extract clusters using
	locally-biased random walks around a user-specified seed node, and are known to have worst-case guarantees for certain graph-based measures of cluster quality.
	In contrast to existing works, 
	we analyze the personalized PageRank (\ppr) algorithm in the classical statistical learning setup,
	where we obtain samples from an unknown distribution, and aim to identify connected
	regions of high-density (density clusters).
	With respect to a neighborhood graph formed over these samples, we provide guarantees for a pair of cluster quality criteria evaluated on empirical analogues to these density clusters. As a result, the \pprspace algorithm is shown to 
	extract sufficiently salient density clusters, and we 
	analyze the sample-complexity of the algorithm.
\end{abstract}

@@

	\item
	\label{asmp: cluster_diameter}
	\textit{Cluster diameter:}
	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
	\begin{equation*}
	\norm{x - x'} \leq D.
	\end{equation*}
\end{enumerate}

@@

We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
\begin{theorem}
	\label{thm: inverse_mixing_time_lower_bound}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then, for any $r < \sigma/4d$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$. Then for
	\begin{equation*}
	\textcolor{red}{n \geq }
	\end{equation*}
	we have
	\begin{equation*}
	\Psi_{n,r}(\Cset[\Xbf]) \geq c_d \frac{r^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
	\end{equation*}
	for \textcolor{red}{$c_d = (1 + \epsilon)$}.
\end{theorem}

>>>>

\begin{abstract}
	Spectral clustering methods are 
	a family of popular non-parametric clustering tools.
	Recent works have proposed and analyzed 
	\emph{local} spectral methods, which 
	extract clusters using
	locally-biased random walks around a user-specified seed node, and are known to have worst-case guarantees for certain graph-based measures of cluster quality.
	In contrast to existing works, 
	we analyze the personalized PageRank (\ppr) algorithm in the classical statistical learning setup,
	where we obtain samples from an unknown distribution, and aim to identify connected
	regions of high-density (density clusters).
	With respect to a neighborhood graph formed over these samples, we provide guarantees for a pair of cluster quality criteria evaluated on empirical analogues to these density clusters. As a result, the \pprspace algorithm is shown to 
	extract sufficiently salient density clusters.
\end{abstract}

@@

	\item
	\label{asmp: cluster_diameter}
	\textit{Cluster diameter:}
	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
	\begin{equation*}
	\norm{x - x'} \leq D,
	\end{equation*}
	and \textcolor{red}{$\Csig$ is a convex set.}
\end{enumerate}

@@

We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
\begin{theorem}
	\label{thm: inverse_mixing_time_lower_bound}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then, for any $r < \sigma/4d$, the following statement holds: with probability one
	\begin{align}
	\label{eqn: inverse_mixing_time_lower_bound}
	\liminf_{n \to \infty} & \Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{d^2D^2}{r^2} \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
	& c_3  + \log \log \mu \bigr) \biggr),
	\end{align}
	where $\mu = \log(\frac{2D}{r})$, $c_1 = 3852800/3$, $c_2 = 331776$, and $c_3 = \log 2$ are all dimension free, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
\end{theorem}
